---
title: "R Notebook"
output: html_notebook
---


Angostura Big Query ETL

Note to user
  - This code uses Angostura to access the database of Medicos Por La Salud.
  - You will need to grant access to Google BigQuery with your google account. 
    - Once you run the code, click yes to grant permission to Google to manage BigQuery.
  - If successfull, it will store the contents of the database in the variable name 'df'.
  - You can then perform the rest of your analysis using the variable 'df'.
    - Create another chunk once the code is exectuted.
    
    
  ** To run the chunk below (i.e the grey region), press Ctrl + Shift + Enter together

```{r}

# Library dependencies
if (!require("bigrquery")) install.packages("bigrquery")

# Authenticate user
bq_auth(path="https://storage.googleapis.com/angostura-public/hult-hackathon-key.json")

# SQL request and store into dataframe
project_id <- "event-pipeline"
sql <- 'SELECT * from `angostura_dev.eh_health_survey_response`'
df <- query_exec(sql, project_id, use_legacy_sql = FALSE)

```

Perform your analysis from this point on..

```{r}

```


